Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-06-18 LaTeX/response.tex

  Furthermore the range of models simulated from is rather limited; for (4) you could simulate from a range of different max-stable processes (even if you don’t fit these, it might be interesting to see how the skew-t model handles them). \\

  \begin{response}
    We have added clarification for these points in the description of the simulation study.
    The parameters in the marginal distribution for all methods were estimated in a fully-Bayesian manner using MCMC methods.
    The constant mean function was chosen somewhat arbitrarily, but permits a common threshold to apply to all sites.
    Finally, we have also added a 5th design to the simulation study using a Brown-Resnick process to generate data, and find that the skew-$t$ method performs similarly to the other setting.
    For this new setting, we find that our model performs similarly to the case in setting (4) with some improvement over the max-stable method for lower quantiles (0.90 -- 0.98), and the max-stable method tends to perform better at more extreme quantiles.
  \end{response}

  It would be nice to see alternative model evaluations to the Brier score, or at least perhaps gain some sense of whether there is strong spatial variation in the score. If the model is much better at predicting in some locations than others, then one may want to be wary of using it in some areas\ldots \\

  \begin{response}
    We agree that maps of Brier scores would be informative.
    This information could conceptually inform future monitor sites.
    We have now added a map of Brier scores (see Web \fref{stfig:bssite}), which shows that performance is similar throughout the US with the most varied performance in California.
  \end{response}

### 2016-06-18 LaTeX/supplemental_rev.tex
manuscript updates

>>>>

\section{Brier scores for ozone prediction} \label{sta:ozonesite}
Because typical ozone concentration varies throughout the US, we have included Brier scores by site for two model fits (Gaussian and Skew-$t$, $K = 5$, $T = 50$) in \fref{stfig:bssite}.
As we can see in these plots, both models seem to perform similarly across the US with the poorest performance in California.
Other methods have similar Brier score maps to these.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{plots/bs-site}
  \caption{Map of Brier scores for Gaussian (top) vs Skew-$t$, $K = 5$, $T = 50$ (bottom).}
  \label{stfig:bssite}
\end{figure}
